---
title: "T-Test Problem"
author: "Your Name"
date: "Spring, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(tigerstats)
Ourdata <- read.csv(file="GSScsv.csv")
```


## Is there a difference in  average years of education (EDUC) between the those who did or did not vote in 2012 (VOTE12)?

$H_0$ There is no difference avarage years of educations between those who voted and those who did not vote in 2012    
$H_A$ There is a difference avarage years of education between those who voted and those who did not vote in 2012   

## Graphical summary
```{r}
plot(EDUC~VOTE12,data=Ourdata)
```


It appears that the average number of years of educations is the same. 



## Numerical Summary 
```{r}
favstats(EDUC~VOTE12,data=Ourdata)
```


## Inferenal Test
```{r}
t.test(EDUC~VOTE12,data=Ourdata)
```

## Conclusion
The p-value from the t-test is 0.004, this is less than 0.05, so we reject the null hypothesis.
 So we conclude we have edvidence to prove that there is a different in the years of education for those who voted in 2012.   
